\documentclass[12pt]{extarticle}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{cite}
\usepackage{multicol}
\usepackage{setspace}
\usepackage{changepage}

\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}{Correlation}[thm]
\newtheorem{defn}{Definition}[section]
\newtheorem{prop}{Preposition}[section]
\newtheorem{lmm}{Lemma}[section]
\newtheorem{conj}{Conjecture}[section]
\newtheorem{exm}{Example}[section]
\newtheorem{rem}{Remark}[section]
\newtheorem{note}{Note}[section]
\newtheorem{alg}{Algorithm}[section]

\setcounter{thm}{1}
\setcounter{cor}{1}
\setcounter{defn}{1}
\setcounter{prop}{1}
\setcounter{lmm}{1}
\setcounter{conj}{1}
\setcounter{exm}{1}
\setcounter{rem}{1}
\setcounter{note}{1}
\setcounter{alg}{1}
\linespread{1.25}

\begin{document}
\section{Introduction}

Recently, I realized that it is of immense difficulty to keep too many open tabs in my mind while doing research. Besides, I believe providing people with better context regarding my research is a rewarding activity, specially when they decide to attend my presentations. Therefore, the idea of a project to keep track of the context of the papers and/or books I study, was born.

These notes are available publically under MIT license.

P.S: \emph{You may find some music recommendations within the text. Click on the link and enjoy!}    
\section{Preliminaries}
This section contains the prerequisites to have a better understanding of the papers.
\subsection{Category Theory}
The main resource(s) for this topic is \cite{Awodey2010-AWOCTA}.
\begin{defn}[Category]
    A \emph{category} consists of the following data:
    \begin{enumerate}
        \item \emph{Objects}: \(A, B, C,\dots\)
        \item \emph{Arrows}: \(f, g, h,\dots\)
        \item For each arrow \(f : A \rightarrow B\), there are given objects \(dom(f)\) \emph{[read: "domain of f"]} and \(cod(f)\) \emph{[read: "codomain of f"]}, respectively, and namely \(A\) and \(B\) in the example above.
        \item Given arrows \(f: A \rightarrow B\) and \(g : B \rightarrow C\) \([dom(f) = cod(f)]\), there is a given arrow \(g \circ f\ : A \rightarrow C \), called the \emph{composition of \(f\) and \(g\)}.
        \item For each object \(A\), there is a given arrow \(1_{A} : A \rightarrow A\), namely the identity arrow of \(A\).
    \end{enumerate}
    which satisfy the following rules:
    \begin{itemize}
        \item \emph{Assoiativity}: \( \forall f : A \rightarrow B, g: B \rightarrow C, h: C \rightarrow D, \ h \circ (g \circ f) = (h \circ g) \circ f\)
        \item \emph{Unit}: \( \forall f : A \rightarrow B, \ f \circ 1_A = f = 1_B \circ f\)
    \end{itemize}
\end{defn}

Mappings between the categories are called \emph{functors}. They map one category to another while preserving its sturcture. 

\begin{defn}[Functors]
    A \emph{functor} \(F : C \rightarrow D\) between categories \(\mathbf{C}\) and \(\mathbf{D}\) is a mapping of objects to objects and arrows to arrows in such a way that:
    \begin{enumerate}
        \item \(F (f: A \rightarrow B) = F(f) : F(A) \rightarrow F(B)\)
        \item \(F(1_A) = 1_{F(A)}\)
        \item \(F(g \circ f) = F(g) \circ F(f)\)
    \end{enumerate}
\end{defn}

\subsection{Nominal Sets}

\section{Papers}

\subsection{An Equational Axiomatization of Dynamic Threads via Algebraic Effects}

This section is dedicated to the notes taken from the paper \emph{An Equational Axiomatization of Dynamic Threads via Algebraic Effects} \cite{10.1145/3776706}.

First we begin with the definition of \emph{Partially Ordered Multisets} or \emph{pomsets}, introduced in \cite{Pratt1986ModelingCW}. The name is self-explanatory for intuition, so we shall proceed to the formal definition.

\begin{defn}[Pomsets]
    A \emph{labeled partial order (LPO)} is a 4-tuple \((V, \Sigma, \leqslant, \mu)\) consisting of 
    \begin{enumerate}
        \item a \emph{vertex set} \(V\), typically modeling \emph{events};
        \item an \emph{alphabet} \(\Sigma\) (for symbol set), typically modeling \emph{actions} such as the arrival of integer 3 t port \(Q\), the transition of pin-13 of IC-7 to 4.5 volts, or the disappearance of the 14.3 MHz component of a signal;
        \item a \emph{partial order} \(\leqslant\) on \(V\), with \(e \leqslant f\) typically being interpreted as event \(e\) necessarily preceding event \(f\) in time; and 
        \item a \emph{labeling function} \(\mu : V \rightarrow \Sigma\) assigning symbols to vertices, each labeled event representing an \(occurrece\) of the action labeling it, with the same action possibly having multiple occurrence (i.e. \(\mu\) need not be injective).
    \end{enumerate}
    A \emph{pomset} is the isomorphism class of an LPO, denoted \([V, \Sigma, \leqslant, \mu]\).
\end{defn}

The key idea of their work is to take thread IDs seriously: their algebraic framework supports abstract names/IDs, as well as binding and passing them. 
Their language consists of the following commands.
\begin{itemize}
    \item \texttt{fork(\(a.x(a), y\))}[of the type \texttt{\(((tid \rightarrow t) \rightarrow t \rightarrow t)\)}]: spawn a new child thread with ID \(a\), run the continuation \(y\) through it while concurrently running continuation \(x\) in the parent thread. The ID of the child is (obviously) passed to the parent thread. You may see the continuation as going on through a code block.
    \item \texttt{wait}: analoguous with the same programming concept.
    \item \texttt{stop}: ends the current thread as soon as it is called, and unblocks all the waiting threads with respect to the one stopped.
    \item \texttt{act}\(_\sigma\): primitive atomic actions like going forward. It's possible to combine this with other algebraic effects (e.g. access to look at concurrent shared memory) but not for now [seems that they also dodge shared memory for the sake of simplicity].
\end{itemize}

The main contribution is a theory with eight equations between the four operations above, and a syntax-free representation theorem of terms modulo equations. They also show that for closed terms, the representation exactly matches the long-established model of true concurrency based on pomsets.

Huh?

Let's dive in.\newline
\textbf{What does fork do?}\\
\textbf{What does fork do?}\\
\textbf{What does fork do?}\\
\textbf{What does fork do?}\\

\subsubsection*{Personal Remarks}
In my honest opinion, this paper is well-written and I would have accepted it, but with a few remarks as below.
\begin{itemize}
    \item They do repeat what they are gonna do as one reads through the paper, and given the length of the paper, it is a good thing to prevent the reader constantly going back to its preliminaries. But they do this a bit untimely, thus the repetitions being scattered throughout the text unevenly.
    \item They explain everything very well altogether but they could do this in a more structured way. sometimes it feels like they indulge a bit too much in their idea.
    \item This paper also suffers from the classic problems of type theory papers, which is dense, complicated notations.
    \item The content is too much for one paper. Maybe they could break it into at least two papers or even three.
\end{itemize}

\bibliographystyle{abbrv}
\bibliography{ref}
\end{document}